Properties of Winning Iterated Prisoner's Dilemma Strategies.

### 2020-04-25 paper/main.tex
cite raw data set
removes TODO

The different tournament types as well as the data collection, made
possible due to an open source library called Axelrod-Python (APL),
are covered in Section~\ref{section:data_collection}. The data set generated  % TODO Modify this when the raw as well as the processed data is archived
for this work has been made publicly available~\cite{data} and can be used
for further analysis and insights.
Section~\ref{section:top_performances}, focuses on the best performing
strategies for each type of tournament and overall.
Section~\ref{section:evaluation_of_performance}, explores the traits which
contribute to good performance, and finally the results are summarised in
Section~\ref{section:conclusion}. This manuscripts uses several parameters,
introduced in the following sections. The full set of
parameters and their definitions are given in Appendix~\ref{app:parameters}.

@@

The data set described in this work contains the largest number of IPD tournaments,
to the authors knowledge, and it available at~\cite{data}. Further data mining % TODO Modify this when the raw data is also archived
could be applied and provide new insights in the field.

>>>>

The different tournament types as well as the data collection, made
possible due to an open source library called Axelrod-Python (APL),
are covered in Section~\ref{section:data_collection}. The raw as well as the processed
data set generated
for this work has been made publicly available~\cite{data, raw_data} and can be used
for further analysis and insights.
Section~\ref{section:top_performances}, focuses on the best performing
strategies for each type of tournament and overall.
Section~\ref{section:evaluation_of_performance}, explores the traits which
contribute to good performance, and finally the results are summarised in
Section~\ref{section:conclusion}. This manuscripts uses several parameters,
introduced in the following sections. The full set of
parameters and their definitions are given in Appendix~\ref{app:parameters}.

@@

The data set described in this work contains the largest number of IPD tournaments,
to the authors knowledge. The raw data set is available at~\cite{raw_data} and the
processed data at~\cite{data}. Further data mining
could be applied and provide new insights in the field.
